A Spatial AR System for Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-10 paper/elsarticle/elsarticle-template.tex
paper

\begin{figure}
    \centerline{\includegraphics[scale=.35]{images/2d3d.png}}
    \caption{Scene plane (gray) recovered via spatial resection with respect to 2D-3D correspondences obtained using a chessboard pattern (blue); 3D circles pattern points obtained by intersection with the scene plane of back-projections (likewise gray) of circles pattern center points detected in the image plane (red). Note that the points in the figure are the points recovered for the projector calibration image in Figure~\ref{fig:2d}(b), acquired by the downwards-facing camera (frustum of the camera in black, with up vector in red).}
    \label{fig:3d}
\end{figure}

>>>>

\begin{figure}
    \centerline{\includegraphics[scale=.35]{images/2d3d.png}}
    \caption{Scene plane (gray) recovered via spatial resection with respect to 2D-3D correspondences obtained using a chessboard pattern (blue); 3D circles pattern points---i.e., the 3D positions of the
2D-3D correspondences to be used for calibrating the projector---obtained by intersection with the scene plane of back-projections (likewise gray) of the 2D circles pattern center points detected in the image plane (red). Note that the points in the figure are the points recovered for the projector calibration image in Figure~\ref{fig:2d}(b), acquired by the downwards-facing camera (frustum of the camera in black, with up vector in red).}
    \label{fig:3d}
\end{figure}
